Sr: Processing Data Streams and Avoiding Work

### 2012-05-04 paper/paper.tex
Add conclusion

>>>>

\section{Conclusion}
I have extended the ideas of approximate computations to a MapReduce-style framework and shown
that it is feasible to tune the input parameters of a job to achieve sufficient precision and
recall for a particular application.

I have taken a different approach to streaming MapReduce by treating data not as a batch, but
as a stream. At any given point in the execution of a job, the collectors will have accurate
(so far as the job parameters allow) results for data seen until that point. This approach
guarantees freshness and makes it easier to incorporate new data into an existing computation,
yet it suffers from being limited to online aggregations.

The Sr source code is open source and available at:
\begin{center}
  \url{https://github.com/lopopolo/sr}
\end{center}
